On finiteness of structures produced deterministically by oritatami co-transcriptional folding \thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~S.}

### 2018-11-09 paper.tex
Update
Theorem 1, more contents added.

\begin{theorem}\label{thm:OS_to_2dTM}
	There exists a Turing machine with 2-dimensional tape that simulates any oritatami system $\Xi = (\Sigma, R, \delta, \alpha, \sigma, w)$ in time $O(((|\sigma| + |w|)\delta)^\delta)$. 
\end{theorem}
\begin{proof}
	Take any step in the computation, up to which some $i \ge 0$ first beads of $w$ have been stabilized, with the last bead at a point $p$. 
	The number of all possible elongations of the current conformation by the next $\delta$-beads is $(6 \times 5^{\delta-1}) \times ((2^4)^{\delta-1} \times 2^5)$. 
\end{proof}

>>>>

\begin{theorem}\label{thm:OS_to_2dTM}
	There exists a Turing machine with 2-dimensional tape that simulates any oritatami system $\Xi = (\Sigma, R, \delta, \alpha, \sigma, w)$ in time ??. 
\end{theorem}
\begin{proof}
	Take any step in the computation, up to which some $i \ge 0$ first beads of $w$ have been stabilized, with the last bead at a point $p$. 
	The number of all possible elongations of the current conformation by the next $\delta$-beads is $(6 \times 5^{\delta-1}) \times ((2^4)^{\delta-1} \times 2^5) \in 2^{O(\delta)}$. 
	We can check for each of these elongations whether its arity is at most $\alpha$ or not and whether it is $R$-valid or not in time $O(\delta)$. 
\end{proof}
